---
title: "Social Survey"
author: "Paul Hamby"
date: "11/13/17"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   
In this analysis, we are observing several different varaibles within the population. As we observe these varibles such as the beleif in the big bang theory, race, and many others, we are interested in seing if there is a relationship between these factors. In other words, does a person's education level have a direct relationship with their beliefs? That is what we are interested in observing when looking at the data from the General Social Survey from the year 2014. As these factors are observed, there may or may not be a direct relationship observed.  

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

In order to give a fair observation, we are going to survey 3,842 people whom will be tested on 1,000 different variables/questions. Despite the General Social Survey having many different varaibles to measure, we are going to only focus on some of the varaibles. The varaibles we are going to be measuring are the following: beleif in the big bang theory, race, education level, and the belief in God. We are using the data from the General Social Survey for the year 2014 because it usually takes time in order for the results to be released. We will be using a varaible analysis test to see if there is a direct correlation between the different beliefs/characteristics of the population. For the numerical method, we are going to be performing a t-test between two varaibles. For the graphical method, I will be using a latrice barchart because, I think it would be ideal for this analysis involving several varaibles. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
rowPerc(race_table)
```
From the YES group, we can see 39% of white said YES to gun ownership, while 17% of the black group stated yes, and 14% of the other group said YES. When observing the NO responses to GUn-ownership, it appears the minority groups had stated No to gun-ownership in comparison to the whites. It appears 61% of whites stated No to gun-ownership while 83% of the black group stated No respectivley. 

```{r}
rowPerc(sex_table)
```

When observing the results from both males and females, we can see there was a slighly higher percent of males that states YES to gun-onwership. About 40% of males said Yes to Gun-onwership, while 27% of women stated Yes. However, both groups had a higher rate of statting NO to gun-ownership, 60% of the response was from Males and 72% made up females. 

```{r}
rowPerc(god_table)
```
When observing the numerical results of the groups, we can see that both the groups who either do or don't believe in God responded very simialry. There was an equal response in YES to Gun-onwership for Atheists, Theists, and Agnostics. Therefore, there is no direct relationship between once stance on GUn-onwership and their belief in God. 

```{r}
rowPerc(polviews_table)
```
When obsverving the numerical results, it appears there was a majoirty of a YES response to gun-ownership from Conservatives at a rate of 42%. While the Liberal group had the lowest response to gun-ownership at a rate of 25%. We can also observe, that Conservatives had the lowest NO response to gun-onwership at a rare of 58%. Liberals had the largest response to gun-onwership at a rate of 75%. 

```{r}
rowPerc(cappun_table)
```
When observing the numerical data for gun-ownership and those who favor captial punishment. We can see there is a difference in reponses. Those who are in favor of gun-ownership are more in favor of capital punishment. We see this evident as there was a 41% YEs rate to capital Punishment (gun owners) and 59% NO rate from those who are opposed to gun-ownership. Therefore, we can see there is a higher yes rate for captial punishment from those who favor gun-onwership than those who do not. 
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
