---
title: "Social Survey"
author: "Paul Hamby"
date: "11/13/17"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   
In this analysis, we are observing several different varaibles within the population. As we observe these varibles such as the beleif in the big bang theory, race, and many others, we are interested in seing if there is a relationship between these factors. In other words, does a person's education level have a direct relationship with their beliefs? That is what we are interested in observing when looking at the data from the General Social Survey from the year 2014. As these factors are observed, there may or may not be a direct relationship observed.  

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

In order to give a fair observation, we are going to survey 3,842 people whom will be tested on 1,000 different variables/questions. Despite the General Social Survey having many different varaibles to measure, we are going to only focus on some of the varaibles. The varaibles we are going to be measuring are the following: beleif in the big bang theory, race, education level, and the belief in God. We are using the data from the General Social Survey for the year 2014 because it usually takes time in order for the results to be released. We will be using a varaible analysis test to see if there is a direct correlation between the different beliefs/characteristics of the population. For the numerical method, we are going to be performing a t-test between two varaibles. For the graphical method, I will be using a latrice barchart because, I think it would be ideal for this analysis involving several varaibles. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
See the Descriptive, Graphical, and Numerical, and Inferential Results sections below:

## Descriptive Results

### Graphical Descriptive Results
Gun Ownership Vs. Race

```{r}
barchartGC(race_table,type="percent", main= "Gun Ownershhip Vs. Race")
```
Based of this graph, it appears there are similar results between the different racial groups. All of the groups said NO on gun-ownership. However, when we observe which group primiarly said yes to gun-ownership, the white racial group had the highest YES percent. However, the majority of the groups had stated NO on gun-ownership. 

Gun-Ownership Vs. Sex
```{r}
barchartGC(sex_table,type="percent", main= "Gun Ownershhip Vs. Sex")
```
Based on the graph, we can see that both males and females do say NO to gun-ownership. However, we can observe that the male group has a higher percentage of participants who said YES to gun-ownership. However, the majority of the two groups said NO to Gun-onwership.


Gun-Ownership Vs. The Belief in God 
```{r}
barchartGC(god_table,type="percent", main= "Gun Ownershhip Vs. Belief in God")
```
Based on the graph, we can see that there is no direct relationship between a person's belief in God and Gun-ownership. All of the groups gave equal responses of both YES and NO to Gun-onwership. Therefore, there is no correlation. 

Gun-Ownership Vs. Political Beliefs 
```{r}
barchartGC(polviews_table,type="percent", main= "Gun Ownershhip Vs. Political Beliefs")
```
Based on the data on the graph, we can see that there is somewhat of a direct relationship between one's political beliefs and their stance on gun-ownership. There was a higher percent of gun-ownership for Conservatives than there was for the Liberals. However, despite that, between the three groups,the majority still stated NO to gun-ownership.

Gun-Ownership Vs. Captial Punishment 

```{r}
barchartGC(cappun_table,type="percent", main= "Gun Ownershhip Vs. Capital Punishment")
```
Based on the graph, we can see there is a difference the the response of those who favor capital punishment and those who do. We can there were more people who were in favor of capital punishment than those who oppose it. However, despite this being evident, the majority of the two groups still said NO to Gun-ownership. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
rowPerc(race_table)
```
From the YES group, we can see 39% of white said YES to gun ownership, while 17% of the black group stated yes, and 14% of the other group said YES. When observing the NO responses to GUn-ownership, it appears the minority groups had stated No to gun-ownership in comparison to the whites. It appears 61% of whites stated No to gun-ownership while 83% of the black group stated No respectivley. 

```{r}
rowPerc(sex_table)
```

When observing the results from both males and females, we can see there was a slighly higher percent of males that states YES to gun-onwership. About 40% of males said Yes to Gun-onwership, while 27% of women stated Yes. However, both groups had a higher rate of statting NO to gun-ownership, 60% of the response was from Males and 72% made up females. 

```{r}
rowPerc(god_table)
```
When observing the numerical results of the groups, we can see that both the groups who either do or don't believe in God responded very simialry. There was an equal response in YES to Gun-onwership for Atheists, Theists, and Agnostics. Therefore, there is no direct relationship between once stance on GUn-onwership and their belief in God. 

```{r}
rowPerc(polviews_table)
```
When obsverving the numerical results, it appears there was a majoirty of a YES response to gun-ownership from Conservatives at a rate of 42%. While the Liberal group had the lowest response to gun-ownership at a rate of 25%. We can also observe, that Conservatives had the lowest NO response to gun-onwership at a rare of 58%. Liberals had the largest response to gun-onwership at a rate of 75%. 

```{r}
rowPerc(cappun_table)
```
When observing the numerical data for gun-ownership and those who favor captial punishment. We can see there is a difference in reponses. Those who are in favor of gun-ownership are more in favor of capital punishment. We see this evident as there was a 41% YEs rate to capital Punishment (gun owners) and 59% NO rate from those who are opposed to gun-ownership. Therefore, we can see there is a higher yes rate for captial punishment from those who favor gun-onwership than those who do not. 
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(race_table)
```
Based of the p-value being low at approximatley 0, it appears that we have to reject the null hypothesis. The null hypothesis therefore is rejected, and there is a direct relationship between race and gun-ownership. 

```{r}
chisqtestGC(sex_table)
```
The P-value is low at approximatley 0, therefore, we have to reject the null hypothesis which states there is no direct relationship between gun ownership and sex. However, in this case, we can see there is a direct relationship as females tend to be more opposed to gun onwership then men. 


```{r}
chisqtestGC(god_table)
```
The P value of 0.97 is very close to the degrees of freedom from the chisqaured test which is 2. Therefore, based on the data, we will have to agree with the null hyptohesis. The null hyptohesis states that there is not a direct relationship between ones beleif in God and gun-onwership.  

```{r}
chisqtestGC(polviews_table)
```
The p-value is at approximatley 0 which means that we have to reject the null hypotheis. The null hypothesis predicted that there would be more of the moderae political group that would be in favor of gun ownership. However, that is not the case as they highest YES rate came from the conservative group. Therefore, we would agree that there is a direct relationship between ones political views and gun ownership. 

```{r}
chisqtestGC(cappun_table)
```
Based on the p-value of 0, it appears that we would have to reject the null hypotheis. The null hypothesis states that there is no direct realtionship between ones views on capital punishment and gun ownership. Therefore, we see there is a direct realtionship between ones views on capital punishment and gun ownership. 
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
In conclusion, when observing gun owernship and comparing the results to several other varaibles, there is evidence supporting a direct relationship. When comparing gun ownership with race, there was a direct relationship as the results showed, the majority of whites stated yes on gun ownership. However, despite this being evident, the majority of the racial groups stated NO on gun ownership. The results amongst the groups of people however varied and were not all directly the same. When observing the results when comparing gun ownership and sex, we also observed a direct realtionship. It appeared that females were more opposed to gun ownership than males. One of the variables did not have a direct relationship wuth gun ownership. When observing the belief in God with gun ownership, we saw that all of the groups responded similarly, regaurdless of their religious beliefs. One explanation for this could be that there may not be an effect on gun ownership on religious beliefs. When observing the different political groups and their view on gun ownership, there was a direct relationship. This may be due to the effect that most conservatives tend to vote more on laws that are in favor of gun-ownership. When looking at the subject of capitial punishment, there appeared to be a direct realtionship. We see this evident as most people who are in favor of gun ownership were also in favor of captial punishment. Therefore, all of the variables had a direct realtionship with gun ownership with the exception with the Belief in God. 