---
title: "Social Survey"
author: "Paul Hamby"
date: "11/13/17"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   
In this analysis, we are observing several different varaibles within the population. As we observe these varibles such as the beleif in the big bang theory, race, and many others, we are interested in seing if there is a relationship between these factors. In other words, does a person's education level have a direct relationship with their beliefs? That is what we are interested in observing when looking at the data from the General Social Survey from the year 2014. As these factors are observed, there may or may not be a direct relationship observed.  

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

In order to give a fair observation, we are going to survey 3,842 people whom will be tested on 1,000 different variables/questions. Despite the General Social Survey having many different varaibles to measure, we are going to only focus on some of the varaibles. The varaibles we are going to be measuring are the following: beleif in the big bang theory, race, education level, and the belief in God. We are using the data from the General Social Survey for the year 2014 because it usually takes time in order for the results to be released. We will be using a varaible analysis test to see if there is a direct correlation between the different beliefs/characteristics of the population. For the numerical method, we are going to be performing a t-test between two varaibles. For the graphical method, I will be using a latrice barchart because, I think it would be ideal for this analysis involving several varaibles. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
Gun Ownership Vs. Race

```{r}
barchartGC(race_table,type="percent", main= "Gun Ownershhip Vs. Race")
```
Based of this graph, it appears there are similar results between the different racial groups. All of the groups said NO on gun-ownership. However, when we observe which group primiarly said yes to gun-ownership, the white racial group had the highest YES percent. However, the majority of the groups had stated NO on gun-ownership. 

Gun-Ownership Vs. Sex
```{r}
barchartGC(sex_table,type="percent", main= "Gun Ownershhip Vs. Sex")
```
Based on the graph, we can see that both males and females do say NO to gun-ownership. However, we can observe that the male group has a higher percentage of participants who said YES to gun-ownership. However, the majority of the two groups said NO to Gun-onwership.


Gun-Ownership Vs. The Belief in God 
```{r}
barchartGC(god_table,type="percent", main= "Gun Ownershhip Vs. Belief in God")
```
Based on the graph, we can see that there is no direct relationship between a person's belief in God and Gun-ownership. All of the groups gave equal responses of both YES and NO to Gun-onwership. Therefore, there is no correlation. 

Gun-Ownership Vs. Political Beliefs 
```{r}
barchartGC(polviews_table,type="percent", main= "Gun Ownershhip Vs. Political Beliefs")
```
Based on the data on the graph, we can see that there is somewhat of a direct relationship between one's political beliefs and their stance on gun-ownership. There was a higher percent of gun-ownership for Conservatives than there was for the Liberals. However, despite that, between the three groups,the majority still stated NO to gun-ownership.

Gun-Ownership Vs. Captial Punishment 

```{r}
barchartGC(cappun_table,type="percent", main= "Gun Ownershhip Vs. Capital Punishment")
```
Based on the graph, we can see there is a difference the the response of those who favor capital punishment and those who do. We can there were more people who were in favor of capital punishment than those who oppose it. However, despite this being evident, the majority of the two groups still said NO to Gun-ownership. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
